{\plant}: A package for modelling forest trait ecology \& evolution

### 2015-05-29 ms.tex
Update SM links to match file to be uploaded

DS Falster was supported by an ARC discovery grant (DP110102086). RG
FitzJohn was supported by the Science and Industry Endowment Fund
(RP04-174). M Westoby was supported by a fellowship from Australian
Research Council.

@@

See attached file \url{vignette_physiology.pdf}

@@

See attached file \url{vignette_demography.pdf}

@@

See attached file \url{vignette_plant.R}

\section{Cohort spacing}\label{sec:cohort-spacing}

See attached file \url{vignette_cohort_spacing.R}

\section{Solving for equilibrium seed rain}\label{sec:equilibrium}

See attached file \url{vignette_equilibrium.R}

@@

See attached file \url{vignette_patch.R}

@@

See attached file \url{vignette_emergent.R}

\section{Calculating fitness in the {\plant}  package}\label{sec:fitness}

See attached file \url{vignette_fitness.R}

>>>>

DS Falster was supported by an ARC discovery grant (DP110102086). RG
FitzJohn was supported by the Science and Industry Endowment Fund
(RP04-174). M Westoby was supported by a fellowship from Australian
Research Council. We thank {\AA} Brn{\"a}nnstr{\"o}m, J Camac, 
A De Roos, U Dieckmann, R Duursma, and J Johansson for helpful discussions.

@@

See attached file \url{vignettes/physiology.pdf}

@@

See attached file \url{vignettes/demography.pdf}

@@

See attached file \url{vignettes/plant.pdf}, knitr source
\url{vignettes/plant.Rmd}, plain source, \url{vignettes/R/plant.R}

\section{Cohort spacing algorithm}\label{sec:cohort-spacing}

See attached file \url{vignettes/cohort_spacing.pdf}, knitr source
\url{vignettes/cohort_spacing.Rmd}, plain source, \url{vignettes/R/cohort_spacing.R}

\section{Finding demographic equilibrium}\label{sec:equilibrium}

See attached file \url{vignettes/equilibrium.pdf}, knitr source
\url{vignettes/equilibrium.Rmd}, plain source, \url{vignettes/R/equilibrium.R}

@@

See attached file \url{vignettes/patch.pdf}, knitr source
\url{vignettes/patch.Rmd}, plain source, \url{vignettes/R/patch.R}

@@

See attached file \url{vignettes/emergent.pdf}, knitr source
\url{vignettes/emergent.Rmd}, plain source, \url{vignettes/R/emergent.R}

\section{Calculating fitness}\label{sec:fitness}

See attached file \url{vignettes/fitness.pdf}, knitr source
\url{vignettes/fitness.Rmd}, plain source, \url{vignettes/R/fitness.R}
